Supplementary Materials: The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-06-24 analysis/analysis.Rmd
Updated header for supp mat to include title and DOI

---
title: "Supplementary Materials"
author: "Peter J. Kohler and Alasdair D. F. Clarke"
date:
output: bookdown::html_document2
---

>>>>

---
title: "Supplementary Materials: The human visual system preserves the hierarchy of 2-dimensional pattern regularity"
author: "Peter J. Kohler and Alasdair D. F. Clarke"
date: 
output: bookdown::html_document2
---

These are the supplementary materials for:

Kohler, P. J., & Clarke, A. D. (2021). The human visual system preserves the hierarchy of 2-dimensional pattern regularity. Proceedings of the Royal Society B: Biological Sciences. 10.1098/rspb.2021.1142
